Items

### 2024-04-12 items.rmd
- updated items file

---
title: "Items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---

>>>>

---
title: "Items"
subtitle: "Data-set: Need for Privacy and Personality"
author: "Tobias Dienlin & Miriam Metzger"
date: "2024-04-05"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output:
#   pdf_document:
#     toc: TRUE
#     toc_depth: 1
bibliography: 
  - "bibliography/references.bib"
---

# Overview

 <!-- - For a pdf of all items, click here. -->
 <!-- - For the actual questionnaire, click here. -->
